Ice sheet mass flows

### 2024-06-24 sankey.tex
Accumulation -> Mass gain
Discharge -> Calving
Show both frontal advance and retreat in same graphic

    \colorlet{water}[rgb]{cyan!75!blue!50!white}
    \colorlet{ice}[rgb]{gray!20!gray!20!gray!20}
    %% \colorlet{air}[rgb]{gray!1!gray!1!gray!1}
    \colorlet{air}{yellow!50}
    \colorlet{red}[rgb]{red!50!orange!75!white}
    \colorlet{black}[rgb]{black!100!black!100!black!100}

    \sankeyset{
      %% comment for gray outline
      draw/.style={
        draw=white,
        line width=0pt,line cap=round,line join=round,
      },
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/33,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-water-horiz/.style={fill/.style={fill=none, right color=ice, left color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-air-horiz/.style={fill/.style={fill=none, left color=ice, right color=air},},
      water-to-air-horiz/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

    \ifthenelse{\Q{vMG} > \Q{vML}} {
      \ifthenelse{\Q{vFRLOSS} > 0}{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vRFZ}/RFZi}}
      }{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\Q{vFRGAIN}/FG, \qq{f0}/f0i, \Q{vRFZ}/RFZi}}
      }
    } {
      \ifthenelse{\Q{vFRLOSS} > 0}{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vML}/MLi, \Q{vRFZ}/RFZi}}
      }{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\Q{vFRGAIN}/FG, \qq{f0}/f0i, \Q{vML}/MLi, \Q{vRFZ}/RFZi}}
      }
    }

    \ifthenelse{\Q{vFRGAIN} > 0}{
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=15mm,xshift=\xoff]FG.left}, anchor=right}
      \sankeystart{FGi}
      \abovelabel{FGi}{Frontal advance}
      \sankeyoutin{FGi}{FG}
    }{}

@@

    % FLa must exist for placement, but only draw lines if > 0
    \ifthenelse{\Q{vFRLOSS} > 0} {
        \sankeynode{name=FLa, quantity=\qq{FL},
          at={[xshift=\xoff]GZa.left}, anchor=right}
        \sankeyoutin{FL}{FLa}
      }{
        \sankeynode{name=FLa, quantity=\qq{FL},
          at={[yshift=0mm]GZa.left}, anchor=right}
      }

@@

    \ifthenelse{\Q{vFRLOSS} > 0} {
      \sankeyadvance[out-red]{FLa}{10mm}
      \sankeyend[out-red]{FLa}
      \belowlabel{FLa}{Frontal retreat}
    }{}

@@

      \node[font=\tiny, anchor=north]
      at ([yshift=0mm,xshift=3mm]MGa.south) {\qq{MGa}: Accumulation};

@@

    \ifthenelse{\Q{vMG} < \Q{vML}}
      {
        %% mass loss
        \sankeynode{name=ML, quantity=\Q{vML},
          at={[xshift=-\xoff]RF.right}, anchor=left} %, angle=-45}
        \abovelabel{ML}{Drawdown}
        \sankeystart[red]{ML}
        \sankeyadvance[red-to-ice]{ML}{5mm}
        \sankeyoutin{ML}{MLi}
      }
      {
        %% mass gain
        \sankeyadvance[ice-to-black]{MGa}{3mm}
        \sankeyend[black]{MGa}
      }

@@

      \belowlabel{RU}{Runoff}
      \belowlabel{BMa}{Basal melting}
      \belowlabel{SUBa}{Submarine melting}
      \belowlabel{D}{Discharge}
      \belowlabel{GZa}{Grounding line retreat}

>>>>

    \colorlet{water}[rgb]{cyan!75!blue!50!white}
    \colorlet{ice}[rgb]{gray!20!gray!20!gray!20}
    %% \colorlet{air}[rgb]{gray!1!gray!1!gray!1}
    \colorlet{air}{yellow!50}
    \colorlet{red}[rgb]{red!50!orange!75!white}
    \colorlet{black}[rgb]{black!100!black!100!black!100}
    \colorlet{gray}[rgb]{black!30!black!30!black!30}

    \sankeyset{
      %% comment for gray outline
      draw/.style={
        draw=white,
        line width=0pt,line cap=round,line join=round,
      },
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/33,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-water-horiz/.style={fill/.style={fill=none, right color=ice, left color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-air-horiz/.style={fill/.style={fill=none, left color=ice, right color=air},},
      water-to-air-horiz/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      black-to-ice/.style={fill/.style={fill=none, bottom color=ice, top color=black},},
      in-black/.style={draw/.style={draw=gray,thick=3},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

    \ifthenelse{\Q{vMG} > \Q{vML}} {
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vFRGAIN}/FG, \Q{vRFZ}/RFZi}}
    } {
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vML}/MLi, \Q{vFRGAIN}/FG, \Q{vRFZ}/RFZi}}
    }

@@

    \sankeynode{name=FLa, quantity=\qq{FL},
      at={[xshift=\xoff]GZa.left}, anchor=right}
    \sankeyoutin{FL}{FLa}

@@

    \sankeyadvance[out-red]{FLa}{10mm}
    \sankeyend[out-red]{FLa}
    \belowlabel{FLa}{Frontal retreat}

@@

      \node[font=\tiny, anchor=north]
      at ([yshift=0mm,xshift=3mm]MGa.south) {\qq{MGa}: Mass gain};

@@

    \ifthenelse{\Q{vMG} < \Q{vML}} {
      %% mass loss
      \sankeynode{name=ML, quantity=\Q{vML},
        at={[xshift=-\xoff]RF.right}, anchor=left} %, angle=-45}
      \abovelabel{ML}{Drawdown}

      % frontal advance next to drawdown (mass loss)
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=-5mm,xshift=-\xoff]ML.right}, anchor=left}

      \sankeystart[red]{ML}
      \sankeyadvance[red-to-ice]{ML}{5mm}
      \sankeyoutin{ML}{MLi}
    }{
      %% mass gain
      \sankeyadvance[ice-to-black]{MGa}{3mm}
      \sankeyend[black]{MGa}

      % frontal with no drawdown
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=15mm,xshift=3mm]RFZi.right}, anchor=left}
    }

    \ifnum \numexpr\qq{FGi} > 0
    \sankeystart[in-black]{FGi}
    \sankeyoutin[in-black]{FGi}{FG}
    \node[font=\tiny, rotate=45, anchor=north east]
    at ([yshift=12mm,xshift=3mm]FGi.right) {Frontal advance: \qq{FGi}};
    \fi

@@

    \belowlabel{RU}{Runoff}
    \belowlabel{BMa}{Basal melting}
    \belowlabel{SUBa}{Submarine melting}
    \belowlabel{D}{Calving}
    \belowlabel{GZa}{Grounding line retreat}
